---
title: "Group 46 CA pollution burden"
author: "Ali Martin and Eva Wilson"
date: "11/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(janitor)
library(here)
library(hexbin)
```

```{r}
ces <-read_csv(here("data","ces3demographics.csv")) %>% 
  clean_names()
```


```{r }
ggplot(data = ces, 
       aes(x = white_percent, 
           y = ces_3_0_score)) + 
  geom_hex() +
  labs(x = "Percent of White Population", 
       y = "CalEnviroScreen 3.0 Score", 
       title = "Relationship Between Percent of White Population and CalEnviroScreen 3.0 score in CA") +
  scale_fill_gradient(low = "paleturquoise1", high = "blue4") +
  theme_minimal()
```

**Figure 1:** The figure above shows the relationship between the percent of white population and pollution burden, which is measured by the aggregate CalEnviroScreen 3.0 score, which  in California. 

Figure 1 indicates that census tracts with a ***smaller*** percentage of white residents generally have higher CalEnviroScreen 3.0 scores, meaning these communities bear a higher pollution burden than the census tracts with a larger percentage of white residents.  

**Data Source:** California Environmental Justice Alliance. 2018. CalEnviroScreen 3.0: A Tool for Advancing Environmental Justice. https://caleja.org/wp-content/uploads/2015/09/CES3.0-5.pdf (Accessed 11/17/2021). For more background and CalEnviroScreen 3.0 maps, visit: https://oehha.ca.gov/calenviroscreen/report/calenviroscreen-30.


